Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-11-26 vesicle_code/docs/permeableVes/main.tex
doing runs

@@

In Figure~\ref{fig:relaxationArea}, we examine the transient dynamics of
four vesicles $\beta = 10^{-3}$ and a variety of initial configurations.
First, in all cases the vesicle eventually reaches a circular shape of
reduced area $\nu=1$. Second, we observe that even though the vesicle is
inflating to a circle, meaning that there is a net flux into the
vesicle, there are regions where the flux is out of the vesicle. These
regions are denoted in blue and are only present at early times.
Finally, the vesicles area does not initially change by much, and
intermediate shapes of semi-permeable vesicles resemble the shape of an
impermeable vesicle. This can be explained by considering the two terms
that contribute to the vesicle velocity: (i) the permeability velocity,
$\beta(\ff \cdot \nn) \nn$, and (ii) the force balance velocity,
$\SS[\ff]$. Since $\beta = 10^{-3}$, the permeability velocity is much
smaller than the force balance velocity at early times, and the
semi-permeable vesicle dynamics resembles those of an impermeable
vesicle. As the force balance velocity decreases, the permeability
velocity dominates, and the vesicle begins to inflate to a circle with
no vanishing force and velocity.

\begin{figure*}[htp]
  \centering
  \input{figures/relaxationArea.tikz}
  \caption{\label{fig:relaxationArea} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady-state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Shear Flow}
We consider a semi-permeable vesicle in the shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
rates $\beta$ and shear rates $\dot{\gamma}$. Depending on its reduced
area and viscosity contrast, two-dimensional vesicles either tank tread
or tumble~\cite{fin-lam-sei-gom2008,kra-win-sei-lip1996}. Since we are
considering semi-permeable vesicles, we assume there is no viscosity
contrast, and tumbling is not possible.
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/shearSS.tikz}
  \fi
%  \includegraphics[width=0.9\linewidth]{figures/shearSS.pdf}
  \caption{\label{fig:shearSS} The reduced area of a semi-permeable
  vesicle in a shear flow. The final reduced area is nearly independent
  of the initial reduced area.}
\end{figure}

In the quiescent flow, the steady state vesicle shape is independent of
the initial vesicle shape. Here we test if a similar results holds with
an imposed flow. In Figure~\ref{fig:shearSS}, we plot the reduced area
of four vesicles with different initial reduced areas. The final shape
depends on the initial vesicle length, but not on its initial reduced
area. Therefore, for this example we only consider vesicles with the
initial reduced area $\nu = 0.65$. For all permeability rates and shear
rates, the semi-permeable vesicle tilts to an inclination angle and
undergoes tank treading dynamics. Because of the semi-permeability, the
initial and final reduced areas differ. In
Figure~\ref{fig:shearPhaseDiagram}, we plot the final shape of the
vesicle for various permeability rates, $\beta$, and shear rates
$\dot{\gamma}$. The shear rate has the largest effect on the final
reduced area.

\begin{figure}[htp]
  \centering
  %\ifTikz
%  \input{figures/shearPhaseDiagramRA2.tikz}
  %\fi
  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and shear rates $\dot{\gamma}$. The final reduced areas are
  reported for the largest and smallest parameter values. The final
  reduced area decreases with the flow rate, while the permeability rate
  has a very small effect on the steady state shape.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. The length
of the vesicle is $L = 2\pi$. We examine the effect of the non-linear
Poiseuille flow on the migration of semi-permeable vesicle. In this
experiment, the vesicle is initialized above the center line $y=0$, and
it migrates towards the center line~\cite{dan-vla-mis2009}. For an
impermeable vesicle, depending on the vesicles reduced area and the flow
rate,  the long time vesicle shape is either an axisymmetric parachute
or bullet, or a asymmetric tank-treading slipper~\cite{kao-bir-mis2009}.
To validate our methods, in
Figure~\ref{fig:parabolicOffCenterImpermeablePhaseDiagram} we
reconstruct the phase diagram for an impermeable
vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
qualitatively agree, Kaoui et al.~report that the vesicles with
$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
axisymmetric. In our simulations these vesicles are slightly asymmetric,
are undergoing a tank treading motion, and we therefore report them as
asymmetric slippers.

\begin{figure}[htp]
%  \ifTikz
%  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
%  \fi
  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseImpermeable.pdf}
  \caption{\label{fig:parabolicOffCenterImpermeablePhaseDiagram} Phase
  diagram of an impermeable vesicle with several different flow rates
  $U$ and reduced areas $\nu$. As shown by Kaoui et
  al.~\cite{kao-bir-mis2009}, the final vesicle shape is either an
  axisymmetric parachute or bullet (pink region) or an asymmetric
  slipper (yellow region).}
\end{figure}

Having validated our method, we investigate the dynamics of a
semi-permeable vesicle in a Poiseuille flow. Using several initial
reduced areas and flow rates, we recreate the impermeable vesicle phase
diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The
final vesicle configurations are in
Figure~\ref{fig:parabolicOffCenterSemipermeablePhaseDiagram}.  As we
observed for the shear flow, the steady state reduced area is
independent of the initial reduced area, and larger flow rates result in
smaller steady state reduced areas. We report the steady state reduced
area in Figure~\ref{fig:parabolicOffCenterSemipermeablePhaseDiagram}.
At the smallest flow rate of $U = 200 \mu m/s$, the steady state reduced
area is large, and the result is an axisymmetric bullet. However, at the
larger flow rates, the steady state reduced area is smaller, and the
result is an asymmetric tank-treading slipper.

\begin{figure}[htp]
%  \ifTikz
%  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
%  \fi
  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseSemipermeable.pdf}
  \caption{\label{fig:parabolicOffCenterSemipermeablePhaseDiagram} Phase
  diagram of a semi-permeable vesicle, with $\beta = 10^{-3}$, with
  several different flow rates $U$ and reduced areas $\nu$. The
  steady state reduced area for each flow rate, which is reported along
  the top of the vesicles, is nearly independent of the initial reduced
  area. Low flow rates result in axisymmetric vesicles with large
  reduced area, and high flow rates result in asymmetric vesicles with
  low reduced area. Results at higher flow rates are not eporeted since
  the vesicle self-intersects.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
We consider the effect of stenosis on a semi-permeable vesicle. To allow
for large amounts of fluid flux through the membrane, we consider
geometry with a long constricted region. We start by considering a
vesicle initialized with reduced area $\nu = 0.65$, and we compare the
vesicle shape when $\beta = 0$ (impermeable) and $\beta = 10^{-3}$
(permeable). Figure~\ref{fig:stenosisShape} shows the vesicles' shape at
several locations along the constriction. The colors along the left
channel represent the tension and those along the right represent the
flux. In Figure~\ref{fig:stenosisTensionAndFlux}, the tension at
location $x=20$ and the flux at location $x=30$ are plotted with respect
to arclength. The value of $\theta=0$ corresponds to the nose of the
vesicle.
\begin{figure}[htp]
%  \ifTikz
%  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension02.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension06.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension10.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
%  \fi
  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension02.pdf}
  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux04.pdf}
  \\
  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension06.pdf}
  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux08.pdf}
  \\
  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension10.pdf}
  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux12.pdf}
  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
  semi-permeable (solid) vesicle in a stenosed geometry (black).
  The vesicles' initial configuration are identical with reduced area
  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
  (right). The semi-permeable vesicle deflates throughout the
  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
  curvature regions than its impermeable counterpart.}
\end{figure}

\begin{figure}[htp]
  \centering
%  \ifTikz
%  \scalebox{0.5}{\input{figures/stenosisTension12.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisFlux12.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisXvelocity12.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisYvelocity12.tikz}}
%  \fi
  \includegraphics[width=0.45\linewidth]{figures/stenosisTension12.pdf}
  \includegraphics[width=0.45\linewidth]{figures/stenosisFlux12.pdf} \\
  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocity12.pdf}
  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocity12.pdf}
  \caption{\label{fig:stenosisTensionAndFlux} The tension (top left), 
  flux (top right), $x$-velocity (bottom left), and $y$-velocity (bottom
  right) of the semi-permeable (red) and impermeable (dashed blue)
  vesicles in Figure~\ref{fig:stenosisShape} at location $x=50$. The
  point $\theta=0$ corresponds to the right-most point of the vesicle.}
\end{figure}

\begin{figure}[htp]
  \centering
%  \ifTikz
%  \input{figures/stenosisArea.tikz}
%  \fi
  \includegraphics[width=0.8\linewidth]{figures/stenosisArea}
  \caption{\label{fig:stenosisArea} The area of a stenosed
  semi-permeable vesicle, with permeability rate $\beta=10^{-3}$. The
  $x$-axis is the $x$-coordinate of the center of mass of the vesicle.
  The vesicle loses fluid at a constant rate throughout the constriction
  that is between $\pm 60$. The semi-permeable vesicle loses 12.8\% of
  its fluid.}
\end{figure}

\begin{figure}[htp]
%  \ifTikz
%  \input{figures/stenosisBL.tikz}
%  \fi
  \includegraphics[width=\linewidth]{figures/stenosisBL.pdf}
  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable (red) and
  imperemable (blue) vesicle. The semi-permeable vesicle has 
  reduced area 0.17, and both vesicles were initialized with reduce area
  $0.20$. The bottom plot shows the velocity relative to the vesicle
  inside the lubrication layer.  The vesicle velocity in the square is
  nearly constant (see Figure~\ref{fig:stenosisRA020Velocity}.}
\end{figure}

\begin{figure}[htp]
  \centering
%  \ifTikz
%  \scalebox{0.5}{\input{figures/stenosisXvelocityRA020.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisYvelocityRA020.tikz}}
%  \fi
  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocityRA020.pdf}
  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocityRA020.pdf}
  \caption{\label{fig:stenosisRA020Velocity} The $x$ (left) and $y$
  (right) velocities of the vesicle in Figure~\ref{fig:stenosisBL}. The
  red lines correspond to the semi-permeable vesicle and the blue dashed
  lines correspond to the impermeable vesicle.}
\end{figure}

Inspired by an experiment that measures the effects of cells on 
dynamical pressure-drop variations along a micrometer-sized
channel~\cite{abk-fai-sto2006}, we consider a numerical experiment where
a semi-permeable vesicle passes through a constriction. We also measure
the pressure-drop variation by measuring the pressure at the inlet and
outlet of the constriction.

In each experiment, we initialize an elliptical vesicle with longest
diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
10^{-1}$Pa. The geometry is similar to an
experiment~\cite{abk-fai-sto2006} where the membrane starts in a channel
with diameter $25\mu$m and passes into a channel with length $45\mu$m
and diameter $5\mu$m (Figure~\ref{fig:stenosisGeom}. We impose a
Poiseuille flow at an inlet and outlet and a no-slip boundary condition
on the upper and lower walls. The flow rate is chosen so that the
residency time of the vesicle in the constriction agrees with the
experimental results.

\begin{figure}[htp]
%  \ifTikz
%  \input{figures/stenosisGeom.tikz}
%  \fi
  \includegraphics[width=\linewidth]{figures/stenosisGeom.pdf}
  \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
  passing through a constriction. The geometry and parameters are chosen
  to replicate the experiments of Abkarian et
  al.~\cite{abk-fai-sto2006}.}
\end{figure}

\begin{figure}[htp]
%  \ifTikz
%  \input{figures/stenosisPressureFluctuation.tikz}
%  \fi
  \includegraphics[width=\linewidth]{figures/stenosisPressureFluctuation.pdf}
  \caption{\label{fig:stenosisPressure} The excess pressure across the
  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
  denote the start and end of the constriction. The results are
  qualitative agreement with~\cite{abk-fai-sto2006}.}
\end{figure}

@@

>>>>

\todo[inline]{This is a dump of information regarding how we
non-dimensionalize}
In each experiment, we initialize an elliptical vesicle with longest
diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
10^{-1}$Pa.

@@

In Figure~\ref{fig:relaxationComposite}, we examine the transient
dynamics of four vesicles $\beta = 10^{-3}$ and a variety of initial
configurations.  First, in all cases the vesicle eventually reaches a
circular shape of reduced area $\nu=1$. Second, we observe that even
though the vesicle is inflating to a circle, meaning that there is a net
flux into the vesicle, there are regions where the flux is out of the
vesicle. These regions are denoted in blue and are only present at early
times.  Finally, the vesicles area does not initially change by much,
and intermediate shapes of semi-permeable vesicles resemble the shape of
an impermeable vesicle. This can be explained by considering the two
terms that contribute to the vesicle velocity: (i) the permeability
velocity, $\beta(\ff \cdot \nn) \nn$, and (ii) the force balance
velocity, $\SS[\ff]$. Since $\beta = 10^{-3}$, the permeability velocity
is much smaller than the force balance velocity at early times, and the
semi-permeable vesicle dynamics resembles those of an impermeable
vesicle. As the force balance velocity decreases, the permeability
velocity dominates, and the vesicle begins to inflate to a circle with
no vanishing force and velocity.

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \fi
  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady-state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Shear Flow}
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/shearComposite.tikz}
  \fi
  \caption{\label{fig:shearComposite} (a) The reduced area of a
  semi-permeable vesicle with $\beta = 10^{-3}$ initialized with four
  different reduced areas in a shear flow with two different flow rates.
  (b) The steady state shape of a semi-permeable vesicle with varying
  flow rates and semi-permeability rates. The circled vesicles
  correspond to the simulations in part (a).}
  \todo[inline]{$\nu=0.75$ run needs more temporal resolution.}
\end{figure*}

We consider a semi-permeable vesicle in the shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
rates $\beta$ and shear rates $\dot{\gamma}$. Depending on its reduced
area and viscosity contrast, two-dimensional vesicles either tank tread
or tumble~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. In our
experiments, tumbling is impossible since we consider semi-permeable
vesicles with no viscosity contrast. Similar to the dynamics of an
impermeable vesicle, a semi-permeable vesicle tilts to an inclination
angle and undergoes tank treading dynamics.

In the quiescent flow, the steady state vesicle shape is independent of
the initial vesicle shape, and we investigate if this is true when a
shear flow is imposed. In Figure~\ref{fig:shearComposite}(a), using four
initial reduced areas and two flow rates, we plot the reduced area of a
semi-permeable vesicle with $\beta = 10^{-3}$. As we saw for the
quiescent example, the final shape does not depend on the initial
reduced area. However, it does depend on the flow rate. We also observe
a very small change in the reduced area at early times with the vesicle
dynamics at early times being similar to those of an impermeable
vesicle.  However, once the vesicle is tank-treading, the normal
component of the force-balance velocity is small and the permeability
velocity dominates and leads to a changing reduced area.

We also form the steady state shape for a variety of semi-permeability
rates and flow rates. Since the final shape is independent of the
initial reduce area, we choose an vesicle with $\nu = 0.65$ for all the
simulations. The steady state vesicle shape, along with its reduced
area, are in Figure~\ref{fig:shearComposite}(b). We see that the flow
rate significantly affects the final vesicle shape, but the
semi-permeability rate has no significant effect. Instead, as we saw in
the quiescent analysis, $\beta$ sets a time scale since the time
required for a vesicle to reach its steady state configuration is
proportional to $\beta^{-1}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
\begin{figure}[htp]
  \ifTikz
  \input{figures/parabolicComposite.tikz}
  \fi
  \caption{\label{fig:parabolicComposite} (a) The steady-state shape of
  an impermeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. The results agree with Kaoui et
  al.~\cite{kao-bir-mis2009}. (b) The steady state shape of a
  semi-permeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates.}
\end{figure}

We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
the effect of the non-linear Poiseuille flow on the migration of
semi-permeable vesicle. In this experiment, the vesicle is initialized
above the center line $y=0$, and it migrates towards the center
line~\cite{dan-vla-mis2009}. For an impermeable vesicle, depending on
the vesicles reduced area and the flow rate, the long time vesicle shape
is either an axisymmetric parachute or bullet, or an asymmetric
tank-treading slipper~\cite{kao-bir-mis2009}. To validate our methods,
in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
for the steady state shape of an impermeable vesicle
vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
qualitatively agree, Kaoui et al.~report that the vesicles with
$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
axisymmetric. In our simulations these vesicles are slightly asymmetric,
are undergoing a tank treading motion, and we therefore report them as
asymmetric slippers.

Having validated our method, we investigate the dynamics of a
semi-permeable vesicle in a Poiseuille flow. Using several initial
reduced areas and flow rates, we recreate the impermeable vesicle phase
diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The
final vesicle configurations are in
Figure~\ref{fig:parabolicComposite}(b). As observed for the shear flow,
the steady state reduced area is independent of the initial reduced
area, and larger flow rates result in smaller steady state reduced
areas. We report the steady state reduced area in
Figure~\ref{fig:parabolicComposite}(b). At the smallest flow rate of $U
= 200 \mu m/s$, the steady state reduced area is large, and the result
is an axisymmetric bullet. At the larger flow rates, the steady state
reduced area is smaller, and the result is an asymmetric tank-treading
slipper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
We consider the effect of stenosis on a semi-permeable vesicle. Inspired
by an experiment that measures the effects of cells on the dynamical
pressure-drop variations along a micrometer-sized
channel~\cite{abk-fai-sto2006}, we first examining the effect of
semi-permeability on the pressure fluctuation across a stenosed
geometry. In this experiment, a pressure drop is used to pass a vesicle
red blood cell (RBC) through a constriction with diameter $5\mu$m and
length $45\mu$m. We set up a similar computational geometry with a
Poiseuille flow imposed at the inlet and outlet
(Figure~\ref{fig:stenosisComposite}(a)). The flow rate is chosen so that
the residency time of the RBC in the constriction agrees with the
experimental results. When the RBC enters the constriction, the result
is an increase in the pressure drop required to maintain a constant flow
rate, and the difference between these pressures is called the excess
pressure. We consider both an impermeable and semi-permeable vesicle
with initial reduced area $\nu = 0.65$ passing through a constricted
geometry and compute the pressure drop between the inlet and outlet of
the constriction. In Figure~\ref{fig:stenosisComposite}(c), we plot the
excess pressures. The impermeable case agrees with experimental
results~\cite{abk-fai-sto2006} (see Figure 3), and the results indicate
that less pressure is required to maintain a constant flow rate when the
vesicle is semi-permeable. Our simulations indicate the
semi-permeability does affect the excess pressure, and the vesicle's
reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a much longer constriction, and we observe that the reduced area
decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).

\begin{figure*}[htp]
  \ifTikz
  \input{figures/stenosisComposite.tikz}
  \fi
  \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
  passing through a constricted geometry similar to the experimental
  device in~\cite{abk-fai-sto2006}. (b) A semi-permeable vesicle passing
  through a constricted geometry that is over five times longer. (c) The
  excess pressure of an impermeable and semi-permeable vesicle in the
  short geometry in (a). (d) The reduced area of the semi-permeable
  vesicle in the short geometry in (a). (e) The reduced area of the
  semi-permeable vesicle in the long geometry in (b). In parts (c), (d),
  and (e), the horizontal axis is the x-coordinate of the vesicle's
  center of mass.}
\end{figure*}

%
%\begin{figure}[htp]
%%  \ifTikz
%%  \input{figures/stenosisGeom.tikz}
%%  \fi
%  \includegraphics[width=\linewidth]{figures/stenosisGeom.pdf}
%  \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
%  passing through a constriction. The geometry and parameters are chosen
%  to replicate the experiments of Abkarian et
%  al.~\cite{abk-fai-sto2006}.}
%\end{figure}
%
%\begin{figure}[htp]
%%  \ifTikz
%%  \input{figures/stenosisPressureFluctuation.tikz}
%%  \fi
%  \includegraphics[width=\linewidth]{figures/stenosisPressureFluctuation.pdf}
%  \caption{\label{fig:stenosisPressure} The excess pressure across the
%  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
%  denote the start and end of the constriction. The results are
%  qualitative agreement with~\cite{abk-fai-sto2006}.}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Contracting Geometry}

@@

% OLD TEXT AND PLOTS FROM THE NUMERICAL EXAMPLES

%\begin{figure}[htp]
%  \centering
%  \ifTikz
%  \input{figures/shearSS.tikz}
%  \fi
%%  \includegraphics[width=0.9\linewidth]{figures/shearSS.pdf}
%  \caption{\label{fig:shearSS} The reduced area of a semi-permeable
%  vesicle in a shear flow. The final reduced area is nearly independent
%  of the initial reduced area.}
%\end{figure}

%\begin{figure}[htp]
%  \centering
%  %\ifTikz
%  \input{figures/shearPhaseDiagramRA2.tikz}
%  %\fi
%%  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
%  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
%  semi-permeable vesicle with several different permeability rates
%  $\beta$ and shear rates $\dot{\gamma}$. The final reduced areas are
%  reported for the largest and smallest parameter values. The final
%  reduced area decreases with the flow rate, while the permeability rate
%  has a very small effect on the steady state shape.}
%\end{figure}

%\begin{figure}[htp]
%%  \ifTikz
%%  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
%%  \fi
%  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseImpermeable.pdf}
%  \caption{\label{fig:parabolicOffCenterImpermeablePhaseDiagram} Phase
%  diagram of an impermeable vesicle with several different flow rates
%  $U$ and reduced areas $\nu$. As shown by Kaoui et
%  al.~\cite{kao-bir-mis2009}, the final vesicle shape is either an
%  axisymmetric parachute or bullet (pink region) or an asymmetric
%  slipper (yellow region).}
%\end{figure}

%\begin{figure}[htp]
%%  \ifTikz
%%  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
%%  \fi
%  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseSemipermeable.pdf}
%  \caption{\label{fig:parabolicOffCenterSemipermeablePhaseDiagram} Phase
%  diagram of a semi-permeable vesicle, with $\beta = 10^{-3}$, with
%  several different flow rates $U$ and reduced areas $\nu$. The
%  steady state reduced area for each flow rate, which is reported along
%  the top of the vesicles, is nearly independent of the initial reduced
%  area. Low flow rates result in axisymmetric vesicles with large
%  reduced area, and high flow rates result in asymmetric vesicles with
%  low reduced area. Results at higher flow rates are not eporeted since
%  the vesicle self-intersects.}
%\end{figure}
%%  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeTension02.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeTension06.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeTension10.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension02.pdf}
%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux04.pdf}
%  \\
%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension06.pdf}
%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux08.pdf}
%  \\
%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension10.pdf}
%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux12.pdf}
%  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
%  semi-permeable (solid) vesicle in a stenosed geometry (black).
%  The vesicles' initial configuration are identical with reduced area
%  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
%  (right). The semi-permeable vesicle deflates throughout the
%  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
%  curvature regions than its impermeable counterpart.}
%%  \scalebox{0.5}{\input{figures/stenosisTension12.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisFlux12.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisXvelocity12.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisYvelocity12.tikz}}
%  \includegraphics[width=0.45\linewidth]{figures/stenosisTension12.pdf}
%  \includegraphics[width=0.45\linewidth]{figures/stenosisFlux12.pdf} \\
%  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocity12.pdf}
%  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocity12.pdf}
%  \caption{\label{fig:stenosisTensionAndFlux} The tension (top left), 
%  flux (top right), $x$-velocity (bottom left), and $y$-velocity (bottom
%  right) of the semi-permeable (red) and impermeable (dashed blue)
%  vesicles in Figure~\ref{fig:stenosisShape} at location $x=50$. The
%  point $\theta=0$ corresponds to the right-most point of the vesicle.}
%%  \input{figures/stenosisArea.tikz}
%  \includegraphics[width=0.8\linewidth]{figures/stenosisArea}
%  \caption{\label{fig:stenosisArea} The area of a stenosed
%  semi-permeable vesicle, with permeability rate $\beta=10^{-3}$. The
%  $x$-axis is the $x$-coordinate of the center of mass of the vesicle.
%  The vesicle loses fluid at a constant rate throughout the constriction
%  that is between $\pm 60$. The semi-permeable vesicle loses 12.8\% of
%  its fluid.}
%%  \input{figures/stenosisBL.tikz}
%  \includegraphics[width=\linewidth]{figures/stenosisBL.pdf}
%  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable (red) and
%  imperemable (blue) vesicle. The semi-permeable vesicle has 
%  reduced area 0.17, and both vesicles were initialized with reduce area
%  $0.20$. The bottom plot shows the velocity relative to the vesicle
%  inside the lubrication layer.  The vesicle velocity in the square is
%  nearly constant (see Figure~\ref{fig:stenosisRA020Velocity}.}
%%  \scalebox{0.5}{\input{figures/stenosisXvelocityRA020.tikz}}
%%  \scalebox{0.5}{\input{figures/stenosisYvelocityRA020.tikz}}
%  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocityRA020.pdf}
%  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocityRA020.pdf}
